Exploring Real Data: A look at AirBnB

### 2017-06-06 ArticleDraft.Rmd
Mathmanda edits up to Beyond the Basics

seattle<-read.csv('Airbnb_Seattle.csv')
currency_to_numeric <- function(x){
  # Convert currencies to numeric i.e. strip dollar signs and commas
  x <- gsub('\\$','', as.character(x))
  x <- gsub('\\,','', as.character(x))
  x <- as.numeric(x)
  return(x)
}
seattle<-seattle %>% mutate(price = currency_to_numeric(price))
```

@@

As Airbnb has grown in popularity a wealth of data has been accumulated about many aspects of the Airbnb experience. One particular independent website, insideairbnb.com, has developed “ … a set of tools and data that allows you to explore how Airbnb is really being used in cities around the world.”  Insideairbnb has gathered public data from Airbnb sites around the world and as mathematicians and statisticians this provides us with a treasure trove of questions to explore!  They have data on cities like Paris, Venice, Amsterdam, Boston, Chicago, Seattle, and many more.  Their data sets include factors such as average reviews, locations, cleaning costs, rent, and much more.

@@

We are located somewhat near Seattle, so for the purposes of discussion we’ll use the Seattle data.  You are welcome to use whichever data set you find most interesting.  The graphical visualization tool allows you to see several descriptive statistics for your chosen city, animate through the frequency and location of reviews, see top rated hosts, and much more.

## Initial Exploratory Data Analysis
<!--As a way to motivate statistical thinking and exploration on these large Airbnb data sets--> Let’s explore a some questions related to your particular city (These explorations are meant to increase in difficulty as you work through them).

### Exploration #2: 
You’re trying to budget your travel money.  In what range of daily prices would you expect the average daily price for a private room at an Airbnb in a particular neighborhood to land?  <!-- **This data isn't normally distributed, so we need to be careful giving confidence intervals for single instances...** -->

**Discussion:** There is a beautiful beach on the Puget Sound in the Alki neighborhood of Seattle.  Let's filter the data to explore the prices from the Alki beach area.  We'll start with some basic descriptive statistics: the average rental price there is $170 but the standard deviation is $97!  The question in this exploration is really asking for a range of prices, and based on the rather large standard deviation, the estimation range will have a rather large range as well.  If this data were normally distributed we would expect *most* of the rentals (~68% of them) to be withing one standard deviation of the mean: between $73 and $267. <!--We expect the price for a rental in the Alkai neighborhood to be somewhere between $140 and $201.  In fact, a 95% confidence interval for the average price in this neighborhood is between $8 and $355!-->  The large variance in the prices leads us to believe that there is more going on here.  Let's create a data visualization to investigate further: 
```{r, echo = F,fig.height = 2,fig.width = 5}
seattle1<-seattle %>% filter(host_neighbourhood == 'Alki')
m = mean(seattle1$price)
s = sd(seattle1$price)
df<-data.frame(id = c(1,1,1,1),x = c(.5,.5,1.5,1.5), y = c(m+s, m-s, m-s, m+s))
ggplot(seattle1, aes(x = 'Alki', y = price)) + geom_violin(fill = 'cyan')+
  geom_segment(x = 0, xend = 1.5, y = m, yend = m, color = 'salmon')+
  geom_segment(aes(x = .5, xend = 1.5, y = m-s, yend = m -s ), lineend = "butt", color = 'Lightpink')+
  geom_segment(aes(x = .5, xend = 1.5, y = m+s, yend = m +s ), lineend = "butt", color = 'Lightpink') + 
  geom_boxplot(width = .4, fill = 'Lightblue')+coord_flip() + xlab('Neighborhood') + 
  ggtitle('Distribution of Prices in the Alki Neighborhood')

#ggplot(seattle1, aes(x = room_type, y = price)) + geom_violin(aes(fill = room_type)) +
#  geom_boxplot(width = .25,aes(fill = room_type ))+coord_flip()

@@

The plot above is called a violin plot.  The curved shape tells us where 'clusters' of the data are located, while the boxplot tells us where the median and quartiles are located.  We observe that this data does *not* appear to be normally distributed. In fact, a relatively low concentration of the rentals in the Alki neighborhood are near the median price; many are between $40 and $80 away from the 'center', in other words, this is a bimodal distribution of data.  We could investigate the types of rentals in this data, or perhaps, their distance from the coastline to figure out what is creating this interesting shape. In addition, if we want to use prices in this neighborhood as part of some further analysis, we might consider performing some kind of variable transformation.  Since the prices here are all greater than zero, bimodal, and fairly "right skewed"", we notice that the distribution is not 'nearly normal' like we have come to expect!  A square root or log transformation might prove useful for further analysis.

### Exploration #3:  
Do you wonder if hosts with cleaner rentals charge more?  How about a more specific question:  is there a statistical difference in daily price between the rentals that are rated most cleanly versus the rentals that are rated least cleanly?

**Discussion:** 
The first order of business in this exploration is to decide what *most cleanly* and *least cleanly* mean to us.  The cleanliness rating scale goes from 0 to 10, but we shouldn't assume that cleanliness ratings are evenly distributed among these numbers, or that the numbers 0-10 represent a linear progression of cleanliness.  In fact, many travelers might feel guilty giving a low cleanliness rating, so we may expect the ratings to be artificially inflated. Having learned from our last exploration, this time let's look at a visualization of the data first.  How about a scatterplot of cleanliness rating versus price?

```{r, echo = F, fig.height=2, fig.width = 5 }
seattle1<- seattle %>% 
  #filter(room_type == 'Private room') %>%
  select(review_scores_cleanliness, price)
seattle1<- seattle1 %>% filter(review_scores_cleanliness != 'N/A')

ggplot(seattle1, aes(x = review_scores_cleanliness, y = price)) + geom_point()+
  ggtitle('Scatterplot') + xlab('Cleanliness Score')
```

One problem with this graphic is that the dots we've plotted are likely hiding information from us! Some of the dots might represent only one observation, while some may have many rental observations which happen to have the same cleanliness review score and price as many others.

One option is to add a ‘jitter’ to our graphic, so that we can see all of our points (or at least get a sense about where our clusters are.

```{r, echo = F, fig.height=2.5 }
#p1<-ggplot(seattle1, aes(x = review_scores_cleanliness, y = price)) + geom_point()+
#  ggtitle('Scatterplot') + xlab('Cleanliness Score')
ggplot(seattle1, aes(x = review_scores_cleanliness, y = price)) +
  geom_jitter(shape = 1) + 
  geom_segment(y = 0, yend = 1000, x = 7.5, xend = 7.5 )+
  ggtitle('Jittered Scatterplot')+ xlab('Cleanliness Score')
#plot_grid(p1,p2,nrow=2)
```

Here we notice that the sample sizes are wildly different: 80 rentals with lower cleanliness ratings and 3,165 with higher ratings.  Perhaps people are just too nice in their ratings or perhaps the Airbnb properties in Seattle are clean! It *looks* like the rentals rated higher for cleanliness get better prices, perhaps with a few outliers. Our scatterplot dots are still so clustered that it makes it hard for us to see what's going on. Let's try one more data visualization.  In the last exploration we looked at a violin plot, and it seemed useful; this time let's look at a side-by-side violin plot. In this case, we've added a log-scale to the price variable, to make the shapes easier to see.

```{r, echo = F, fig.height = 2.5}

seattle1 <- seattle1 %>% mutate(HiLo = ifelse(review_scores_cleanliness>=8, 'High', 'Low'))

#ggplot(seattle1, aes(x = HiLo, y = price, fill = HiLo))+
#  geom_violin()+geom_boxplot( width = .4)+coord_flip()+
#  theme(legend.position = "none")+
  #scale_y_log10() + 
#  xlab('Cleanliness Rating') + ylab('Price')+ggtitle('Regular Scale')

ggplot(seattle1, aes(x = HiLo, y = price, fill = HiLo))+
  geom_violin()+geom_boxplot( width = .4)+coord_flip()+
  theme(legend.position = "none")+
  scale_y_log10() + 
  xlab('Cleanliness Rating') + ylab('Price')+ggtitle('Price on a Log Scale')

#ggplot(seattle1, aes(fill = HiLo, x = price))+stat_density()+
#  scale_x_log10() + ylab('Cleanliness Rating') + xlab('Price')+ggtitle('Distribution #of Daily Prices for High and Low Cleanliness Ratings')

 We see that actually, the bulk of the rental prices for *both* High and Low ratings fall below \$250, but the high rentals have some 'outlier' observations with much higher prices.  On the whole, though, the average rental in either category doesn't appear to be much different. If we conduct a statistical $t$-test on two means, we come to roughly the same conclusion (with a p-value of about 0.26), so there doesn't appear to be strong evidence of a difference in price between the two groups.  <!--At least we know that if we stay at an Airbnb rental with a higher cleanliness rating we aren’t likely being charged more.  -->

```{r, eval = F, echo = F}
# Difference of means test:

summ<-seattle1 %>% group_by(HiLo) %>% 
  summarise(m = mean(price), s = sd(price), n = n())
summ
xbardiff = summ[[1,2]] - summ[[2,2]]
stderror = sqrt(summ[[1,3]]^2/summ[[1,4]] + summ[[2,3]]^2/summ[[2,4]])
tstat = xbardiff/stderror
2*pt(-tstat,9)
```

@@

**Discussion:** Let’s say that we want to stay on the waterfront in Seattle so we’ll compare Alki beach and Belltown; both of which are on the water.

```{r, echo = F, fig.height=2.5}
seattle1<-seattle %>% select(cancellation_policy, host_neighbourhood)

seattle1<- seattle1 %>% filter( (host_neighbourhood == 'Alki' | 
                                      host_neighbourhood == 'Belltown'))

ggplot(seattle1, aes(x = host_neighbourhood, fill = cancellation_policy)) + 
  geom_bar(position = 'fill') + coord_flip() + ylab('Proportion')+ xlab('Neighborhood')+
  ggtitle('Cancellation Policy in Two Neighborhoods')
```

The visualization above shows us the distribution of cancellation policies in the two neighborhoods, and a statistical test on the difference of the  proportions of `strict policies` in each neighborhood gives us a p-value around .0004, and we  conclude that there is evidence to suggest that rentals in Belltown have a much stricter cancellation policy than those in Alki.  The safe bet seems to be Alki, but if we want to spend our social time in downtown we now need to consider the transportation costs.

```{r, include = F}
# Difference of proportions test:
mytable1<-seattle1 %>% filter(cancellation_policy=='strict')%>%
  group_by(host_neighbourhood) %>% tally()
mytable2<-seattle1 %>% group_by(host_neighbourhood) %>% tally()
mytable1
mytable2
p1hat= mytable1[[1,2]]/mytable2[[1,2]]
p2hat= mytable1[[2,2]]/mytable2[[2,2]]
phatdiff = p1hat - p2hat
ppooled = (mytable1[[1,2]]+mytable1[[2,2]])/(mytable2[[1,2]]+mytable2[[2,2]])
stderror = sqrt(ppooled*(1-ppooled)*(1/mytable2[[1,2]]+1/mytable2[[2,2]]))
tstat = phatdiff/stderror
2*pnorm(tstat)

seattle1<-seattle %>% select(cancellation_policy, neighbourhood_cleansed)

seattle1<- seattle1 %>% filter( (neighbourhood_cleansed == 'Alki' | 
                                      neighbourhood_cleansed == 'Belltown'))

ggplot(seattle1, aes(x = neighbourhood_cleansed, fill = cancellation_policy)) + 
  geom_bar(position = 'fill') + coord_flip() + ylab('Proportion')+ xlab('Neighborhood')+
  ggtitle('Cancellation Policy in Two Neighborhoods')

mytable1<-seattle1 %>% filter(cancellation_policy=='strict')%>%
  group_by(neighbourhood_cleansed) %>% tally()
mytable2<-seattle1 %>% group_by(neighbourhood_cleansed) %>% tally()
mytable1
mytable2
p1hat= mytable1[[1,2]]/mytable2[[1,2]]
p2hat= mytable1[[2,2]]/mytable2[[2,2]]
phatdiff = p1hat - p2hat
ppooled = (mytable1[[1,2]]+mytable1[[2,2]])/(mytable2[[1,2]]+mytable2[[2,2]])
stderror = sqrt(ppooled*(1-ppooled)*(1/mytable2[[1,2]]+1/mytable2[[2,2]]))
tstat = phatdiff/stderror
pvalue = 2*pnorm(tstat)

#p-value = 9.214435e-05

@@

```{r,echo = F, fig.height = 2.5,message = F, warnings = FALSE}
seattle1<-seattle %>% select(price, beds)
seattle1<-na.omit(seattle1)
#ggpairs(airbnb6)

seattle1<-seattle1 %>%filter(beds<=14)

p1<-ggplot(seattle1, aes(x = beds, y = price)) + geom_jitter(shape = 1) + xlim(0,11)+
  #ggtitle('Price versus Number of Beds')#+ 
  geom_smooth(method = 'lm',se = F)

#p1
#ggplot(seattle1, aes(x = beds, y = price)) + 
#  stat_density2d(aes(fill = ..level..), geom="polygon")+
#  xlim(0.5,11)+ylim(0,1000)

p2<-ggplot(seattle1, aes(x = beds, y = price)) + 
  stat_density2d(na.rm=TRUE) + xlim(0.5,3.5) +ylim(0,250)
  #geom_smooth(method = 'lm')+
  #ggtitle('2D Density Contours')

plot_grid(p1, p2)
m1<-with(lm(price~beds), data = seattle1)
s<-summary(m1)
#kable(s$coefficients)

@@

A simple linear regression tells us that the best-fit line for our data is approximately $Price = \$46 + 47\cdot beds$, 
so, I should expect to pay about \$93 for a rental with one bed and \$47 more per additional bed. As an additional exploration, you might try find a 95% confidence interval for the true slope (marginal price) of this regression line.  What about a 95% confidence interval for the average price of rentals with 3 beds?  What about a predicted interval for the *actual* price of a rental with 3 beds?  (How are these questions different from each other?)

@@

## Moving Beyond the Basics 
In this section we pose more questions and leave the investigations open to you. If you would like to see how we answered these questions wth the Seattle data, you can visit our workfile at mathquest.carroll.edu/AirbnbExplorations/.  Several of these exercises suggest more advanced techniques, such as multiple regression, logistic regression, or machine learning techniques to answer.  A good idea for each of the following explorations would be to split your data into a training and a test set so that you can test your predictions on data that your model has not seen.  As you work on these explorations consider the following questions: Which variables turn out to be the most important?  The least inportant?  Are there any variables that amount to just 'noise' in this analysis?  How reliable do you think your model is?  Do you think this same model would work in other regions of the world?  Why or why not? Do you think it would be necessary to pre-process that data in any way? <!--For example, do you think that it would be necessary to do a principal component analysis on your data first in order to reduce the dimension of the data set?-->  Do you think that the variables should be transformed in any way? Do you think any additional features should be included in your data (e.g. the square of a feature, the product of two features, etc)?

@@

```{r, echo = F, eval = F}
seattle1<-seattle %>% select(price, accommodates, beds, bathrooms,
                            guests_included,review_scores_rating, neighbourhood_cleansed)

@@

```{r, eval = F, echo = F}
#================== Use Multiple Logistic Regression =====================

@@

```{r, eval = F, echo = F}

>>>>

seattle<-read.csv('Airbnb_Seattle.csv')
currency_to_numeric <- function(x){
  # Convert currencies to numeric i.e. strip dollar signs and commas
  x <- gsub('\\$','', as.character(x))
  x <- gsub('\\,','', as.character(x))
  x <- as.numeric(x)
  return(x)
}
seattle<-seattle %>% mutate(price = currency_to_numeric(price))
showcode<-F
```

Data is seemingly everywhere these days, and is becoming more powerful as we learn how to use it to answer important questions. In this article we highlight one freely-available, rich and complex data set which you might use to try out asking and answering data-driven questions.

@@

As Airbnb has grown in popularity, a wealth of data has been accumulated about many aspects of the Airbnb experience. One particular independent website, insideairbnb.com, has developed “ … a set of tools and data that allows you to explore how Airbnb is really being used in cities around the world.”  Insideairbnb has gathered public data from Airbnb sites around the world and <!--as mathematicians and statisticians--> this provides us with a treasure trove of questions to explore!  <!--They have data on cities like Paris, Venice, Amsterdam, Boston, Chicago, Seattle, and many more.  Their data sets include factors such as average reviews, locations, cleaning costs, rent, and much more.  -->

@@

We are located somewhat near Seattle, so, for our discussions, we’ll use the Seattle data.  You are welcome to use whichever data set you find most interesting.  The graphical visualization tool allows you to see several descriptive statistics for your chosen city, animate through the frequency and location of reviews, see top rated hosts, and much more.

## Initial Exploratory Data Analysis
<!--As a way to motivate statistical thinking and exploration on these large Airbnb data sets--> Let’s explore some questions related to your particular city (These explorations are meant to increase in difficulty as you work through them).

### Exploration #2: 
You’re trying to budget your travel money.  Give a *pracical* estimate for the daily prices of an Airbnb rentals in a particular neighborhood.  <!-- In what range of daily prices would you expect the average daily price for a private room at an Airbnb in a particular neighborhood to land?  **This data isn't normally distributed, so we need to be careful giving confidence intervals for single instances...** -->

**Discussion:** There is a beautiful beach on the Puget Sound in the Alki neighborhood of Seattle.  Let's filter the data to explore the prices of rentals from the Alki beach area.  We'll start with some basic descriptive statistics: the average rental price there is $172 but the standard deviation is $97!  The question in this exploration is best answered with a range of prices, and, based on the rather large standard deviation, the estimate will have a rather large range as well.  If this data were normally distributed we would expect *most* of the rentals (~68% of them) to be withing one standard deviation of the mean: between $75 and $269. <!--We expect the price for a rental in the Alkai neighborhood to be somewhere between $140 and $201.  In fact, a 95% confidence interval for the average price in this neighborhood is between $8 and $355!-->  The large variance in the prices leads us to believe that there is more going on here.  Let's create a data visualization to investigate further:

```{r, echo = showcode,fig.height = 2,fig.width = 5}
#First we filter our data so that only includes the neighbourhood we care about: 
seattle1<-seattle %>% filter(neighbourhood_cleansed == 'Alki')

#Calculate the mean and standard deviation:
m = mean(seattle1$price)
s = sd(seattle1$price)

#Create a boxplot + violin plot to see what prices happen most: 
ggplot(seattle1, aes(x = 'Alki', y = price)) + geom_violin(fill = 'cyan')+
  geom_boxplot(width = .3, fill = 'Lightblue')+coord_flip() + xlab('') + ylab('Price')+
  ggtitle('Distribution of Prices in the Alki Neighborhood')
```

@@

The plot above is called a violin plot.  The curved shape tells us where 'clusters' of the data are located, while the boxplot tells us where the median and quartiles are.  We observe that this data does *not* appear to be normally distributed. In fact, a relatively low concentration of the rentals in the Alki neighborhood are near the mean price; many are between $40 and $100 away from the 'center'.  You may want to investigate the types of rentals in this data, or perhaps, their distance from the coastline to figure out what is creating this interesting shape. In addition, if we want to use prices in this neighborhood as part of some further analysis, we might consider performing a variable transformation.  Since the prices here are all greater than zero, bimodal, and fairly "right skewed" a square root or log transformation might prove useful for further analysis.

### Exploration #3:  
Do you wonder if hosts with cleaner rentals charge more?  Here is a more specific question:  is there a significant difference between the daily price of the *cleanest* rentals verus the *least clean* rentals?

**Discussion:** 
The first order of business in this exploration is to decide what *cleanest and *least clean* mean to us.  The cleanliness rating scale goes from 0 to 10, but we shouldn't assume that cleanliness ratings are evenly distributed among these numbers, or even that the numbers 0-10 represent a linear progression of cleanliness.  In fact, many travelers might feel guilty giving a low cleanliness rating, so we may expect the ratings to be artificially inflated. Having learned from our last exploration, this time let's look at a visualization of the data first.  How about a scatterplot of cleanliness rating versus price?

```{r, echo = showcode, fig.height=2, fig.width = 5 }
#For simplicity, let's eliminate all variables except cleanliness score and price
# and eliminate any missing data
# .... though .... we should consider what missing data might mean about a rental ...
seattle1<- seattle %>% 
  select(review_scores_cleanliness, price)%>%
  filter(review_scores_cleanliness != 'N/A')

#Make a scatterplot of cleanliness rating versus price: 
ggplot(seattle1, aes(x = review_scores_cleanliness, y = price)) + geom_point()+
  ggtitle('Scatterplot') + xlab('Cleanliness Score') + ylab('Price')
```

One problem with this graphic is that the dots we've plotted are likely hiding the very information we want! <!--Some of the dots might represent only one observation, while some may have many rental observations which happen to have the same cleanliness review score and price as many others. --> We assume that every dot we see represents one rental, but there may be places in this scatterplot where many dots all landed on top of each other.

One option is to add a ‘jitter’ to our graphic, so that we can see all (or, at least, more) of our points, which will help us get a sense about where our clusters are.

```{r, echo = showcode, fig.height=2.5 }
# We make a jittered scatterplot, and indicate a potential cut-off value for 
# cleanest vs least clean: 
ggplot(seattle1, aes(x = review_scores_cleanliness, y = price)) +
  geom_jitter(shape = 1) + 
  geom_segment(y = 0, yend = 1000, x = 7.5, xend = 7.5 , color = 'red')+
  ggtitle('Jittered Scatterplot')+ xlab('Cleanliness Score')+ ylab('Price')
```

The jittered scatterplot suggests that 7 might be a good *cut-off* value for separating clean and unclean rentals. Notice that the sample sizes are wildly different: 80 rentals with lower cleanliness ratings and 3,165 with higher ratings.  <!--Perhaps people are just too nice in their ratings or perhaps the Airbnb properties in Seattle are clean!--> It *looks* like the rentals rated higher for cleanliness get better prices, perhaps with a few outliers. However, our scatterplot dots are still so clustered that it makes it hard for us to see what's going on. Let's try <!--one more data visualization.  In the last exploration we looked at a violin plot, and it seemed useful; this time let's look at--> a side-by-side violin plot. In this case, we've added a log-scale to the price variable, to make the shapes easier to see.

```{r, echo = showcode, fig.height = 2.5}
#Let's create a new variable that separates the clean from the unclean!
seattle1 <- seattle1 %>% mutate(HiLo = ifelse(review_scores_cleanliness>=8, 'High', 'Low'))

#Now we make side by side violin and boxplots, so we can compare prices 
#of the two groups: 
ggplot(seattle1, aes(x = HiLo, y = price, fill = HiLo))+
  geom_violin()+geom_boxplot( width = .4)+coord_flip()+
  theme(legend.position = "none")+
  scale_y_log10() + 
  xlab('Cleanliness Rating') + ylab('Price')+ggtitle('Price on a Log Scale')
```

 We see that actually, the bulk of the rental prices for *both* High and Low ratings are centered near $100, but the high rentals have some 'outlier' observations with much higher prices.  On the whole, though, the average rental price in either category doesn't appear to be drastically different. If we conduct a statistical $t$-test on two means, we come to roughly the same conclusion (with a p-value of about 0.23), so there doesn't appear to be strong evidence of a difference in price between the two groups.  <!--At least we know that if we stay at an Airbnb rental with a higher cleanliness rating we aren’t likely being charged more.  -->

```{r, eval = F, echo = showcode}
#Let's look at a few descriptive statistics for our data: 
summ<-seattle1 %>% group_by(HiLo) %>% 
  summarise(m = mean(price), s = sd(price), n = n())
summ

# Difference of means test:
Clean<- seattle1 %>% filter(HiLo =='High')
Unclean<- seattle1 %>% filter(HiLo =='Low')
test<-t.test(Clean$price, Unclean$price)
test
```

@@

**Discussion:** Let’s say that we want to stay on the waterfront in Seattle so we’ll compare Alki beach and Belltown, both of which are on the water.

```{r, echo = showcode, fig.height=2.5}
#Let's eliminate all variables except neighbourhood and cancellation policies,
# and filter out the irrelevant neighbourhoods.
seattle1<-seattle %>%
  select(cancellation_policy,neighbourhood_cleansed)%>%
  filter( (neighbourhood_cleansed == 'Alki' |  neighbourhood_cleansed == 'Belltown'))

#Create a visualization showing the different distributions of cancellation policies
ggplot(seattle1, aes(x = neighbourhood_cleansed, fill = cancellation_policy)) + 
  geom_bar(position = 'fill') + coord_flip() + ylab('Proportion')+ xlab('Neighborhood')+
  ggtitle('Cancellation Policy in Two Neighborhoods')
```

The visualization above shows us the distribution of cancellation policies in the two neighborhoods, and a statistical test on the difference of the  proportions of *strict* policies in each neighborhood gives us a p-value much less than .01, and we  conclude that there is evidence to suggest that rentals in Belltown have a much stricter cancellation policy than those in Alki.  The safe bet seems to be Alki, but if we want to spend our social time in downtown we now need to consider the transportation costs.

```{r, echo = showcode, eval = F}
#Descriptive statistics: 
mytable1<-seattle1 %>% filter(cancellation_policy=='strict')%>%
  group_by(neighbourhood_cleansed) %>% tally()
mytable2<-seattle1 %>% group_by(neighbourhood_cleansed) %>% tally()
x1<-mytable1[[1,2]]
x2<-mytable1[[2,2]]
n1<-mytable2[[1,2]]
n2<-mytable2[[2,2]]
p1hat= x1/n1
p2hat= x2/n2

#Difference of proportions tests:

#Parametric (Z-test)
phatdiff = p1hat - p2hat
ppooled = (x1+x2)/(n1+n2)
stderror = sqrt(ppooled*(1-ppooled)*(1/n1+1/n2))
tstat = phatdiff/stderror
pvaue<- 2*pnorm(tstat)

#Nonparametric (Chi-Squared-test)
prop.test(x = c(x1,x2), n = c(n1,n2))

@@

```{r,echo = showcode, fig.height = 2.5,message = F, warnings = FALSE}
#Let's 
# - eliminate all variables except price and # of beds
# - eliminate missing data (... but worry about what missing data means...)
seattle1<-seattle %>% 
  select(price, beds) %>%
  na.omit()%>%
  filter(beds<=14)

#Create a jittered scatterplot which also shows the best fit line: 
p1<-ggplot(seattle1, aes(x = beds, y = price)) + geom_jitter(shape = 1) + xlim(0,11)+
  geom_smooth(method = 'lm',se = F) + xlab('# of Beds') + ylab('Price')

#Create a contour plot to show where data is most dense: 
p2<-ggplot(seattle1, aes(x = beds, y = price)) + 
  stat_density2d(na.rm=TRUE) + xlim(0.5,3.5) +ylim(0,250)+
  xlab('# of Beds') + ylab('Price')

plot_grid(p1, p2)

#Simple linear regression: 
m1<-with(lm(price~beds), data = seattle1)
s<-summary(m1)
#kable(s$coefficients)

@@

A simple linear regression tells us that the best-fit line for our data is approximately

\[
\text{Price  in \$}= \$46 + \frac{\$47}{\text{bed}} \cdot\left( \text{\# of beds}\right), 
\]

so, I should expect to pay about \$93 for a rental with one bed and \$47 more per additional bed. You might next want to try find a 95% confidence interval for the true slope (marginal price) of this regression line.  What about a 95% confidence interval for the average price of rentals with 3 beds?  What about a predicted interval for the *actual* price of a rental with 3 beds?  (How are these questions different from each other?)

@@

## Moving Beyond the Basics 
In this section we pose more questions and leave the investigations open to you. If you would like to see how we answered these questions wth the Seattle data, you can visit our workfile at mathquest.carroll.edu/AirbnbExplorations/.  Several of these exercises suggest more advanced techniques, such as multiple regression, logistic regression, or machine learning techniques to answer.  A good idea for each of the following explorations would be to split your data into a training and a test set so that you can test your predictions on data that your model has not seen.

As you work on these explorations consider the following questions:

  * Which variables turn out to be the most important?  The least important? 
  * Are there any variables that amount to just 'noise' in this analysis?
  * How reliable do you think your model is?  
  * Do you think this same model would work in other regions of the world?  Why or why not? 
  * Do you think it would be necessary to pre-process that data in any way? <!--For example, do you think that it would be necessary to do a principal component analysis on your data first in order to reduce the dimension of the data set?-->  
  * Do you think that the variables should be transformed in any way? 
  * Do you think any additional features should be included in your data (e.g. the square of a feature, the product of two features, etc)?

@@

```{r, echo = showcode, eval = F}
seattle1<-seattle %>% select(price, accommodates, beds, bathrooms,
                            guests_included,review_scores_rating, neighbourhood_cleansed)

@@

```{r, eval = F, echo = showcode}
#================== Use Multiple Logistic Regression =====================

@@

```{r, eval = F, echo = showcode}
